Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-05 manuscript_results.Rmd
update

  Models = rep(c("AUTO_AR_Lg", "ES27_AR_Lg", "ES64_AR_Lg", "AUTO_ADJ_Lg", "ES27_ADJ_Lg", "ES64_ADJ_Lg", "AUTO_TMP_Lg", "ES27_TMP_Lg", "ES64_TMP_Lg", "AUTO_EPI_Lg", "ES27_EPI_Lg", "ES64_EPI_Lg", "AUTO_AVG_Lg", "ES27_AVG_Lg", "ES64_AVG_Lg"), each=48, times = 4),

@@

            W4_Lg$AUTO_AR_Lg, W4_Lg$ES27_AR_Lg, W4_Lg$ES64_AR_Lg, 
            W4_Lg$AUTO_ADJ_Lg, W4_Lg$ES27_ADJ_Lg, W4_Lg$ES64_ADJ_Lg, 
            W4_Lg$AUTO_TMP_Lg, W4_Lg$ES27_TMP_Lg, W4_Lg$ES64_TMP_Lg, 
            W4_Lg$AUTO_EPI_Lg, W4_Lg$ES27_EPI_Lg, W4_Lg$ES64_EPI_Lg,
            W4_Lg$AUTO_AVG_Lg, W4_Lg$ES27_AVG_Lg, W4_Lg$ES64_AVG_Lg)

@@

# Create a custom color mapping for each variable
custom_colors <- c(
  "AUTO_AR_Lg" = colors_ar[1], "ES27_AR_Lg" = colors_ar[2], "ES64_AR_Lg" = colors_ar[3],
  "AUTO_EPI_Lg" = colors_epi[1], "ES27_EPI_Lg" = colors_epi[2], "ES64_EPI_Lg" = colors_epi[3],
  "AUTO_TMP_Lg" = colors_tmp[1], "ES27_TMP_Lg" = colors_tmp[2], "ES64_TMP_Lg" = colors_tmp[3],
  "AUTO_ADJ_Lg" = colors_adj[1], "ES27_ADJ_Lg" = colors_adj[2], "ES64_ADJ_Lg" = colors_adj[3],
  "AUTO_AVG_Lg" = colors_avg[1], "ES27_AVG_Lg" = colors_avg[2], "ES64_AVG_Lg" = colors_avg[3]
)

>>>>

  Models = rep(c("AUTO_AR_LB", "ES27_AR_LB", "ES64_AR_LB", "AUTO_ADJ_LB", "ES27_ADJ_LB", "ES64_ADJ_LB", "AUTO_TMP_LB", "ES27_TMP_LB", "ES64_TMP_LB", "AUTO_EPI_LB", "ES27_EPI_LB", "ES64_EPI_LB", "AUTO_AVG_LB", "ES27_AVG_LB", "ES64_AVG_LB"), each=48, times = 4),

@@

            W4_Lg$AUTO_AR_Lg, W4_Lg$ES27_AR_Lg, W4_Lg$ES64_AR_Lg, 
            W4_Lg$AUTO_ADJ_Lg, W4_Lg$ES27_ADJ_Lg, W4_Lg$ES64_ADJ_Lg, 
            W4_Lg$AUTO_TMP_Lg, W4_Lg$ES27_TMP_Lg, W4_Lg$ES64_TMP_Lg, 
            W4_Lg$AUTO_EPI_Lg, W4_Lg$ES27_EPI_Lg, W4_Lg$ES64_EPI_Lg,
            W4_Lg$AUTO_AVG_Lg, W4_Lg$ES27_AVG_Lg, W4_Lg$ES64_AVG_Lg)
)

@@

# Create a custom color mapping for each variable
custom_colors <- c(
  "AUTO_AR_LB" = colors_ar[1], "ES27_AR_LB" = colors_ar[2], "ES64_AR_LB" = colors_ar[3],
  "AUTO_EPI_LB" = colors_epi[1], "ES27_EPI_LB" = colors_epi[2], "ES64_EPI_LB" = colors_epi[3],
  "AUTO_TMP_LB" = colors_tmp[1], "ES27_TMP_LB" = colors_tmp[2], "ES64_TMP_LB" = colors_tmp[3],
  "AUTO_ADJ_LB" = colors_adj[1], "ES27_ADJ_LB" = colors_adj[2], "ES64_ADJ_LB" = colors_adj[3],
  "AUTO_AVG_LB" = colors_avg[1], "ES27_AVG_LB" = colors_avg[2], "ES64_AVG_LB" = colors_avg[3]
)
